The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
reorg interpret points into results/discussion

<!--
## Each metric's interpretation

**[JWT: Do we need to define degree first since degree is mentioned in so many of our definitions?]**
* Degree: the number of direct connections an individual has to other individuals in the network. High degree = connected to many indviduals in a single layer. Low degree = not connected to many individuals in a single layer.

@@

* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
* decreasing winter lichen relevance because the degree + number of edges decreased

@@

<!-- RO first sentence... -->

(ref:nobs) Varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open. *There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**. B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations. C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers. D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.

* common, though at different points - more observations until stabilizing
* we dont see the stabilizing/full plateau for connective redundancy but appears to be coming.. 
* still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations

@@

* increasing window length = increasingly similar layers and increasingly redundant edges. more individuals have the opportunity to interact
* increasing window length also leads to increasing similarity between seasons because seasons are less well defined/include more shoulder seasons
* decreasing graph strength at the upper end of window length in winter showing again inclusion of more shoulder season
* layers are more similarly relevant at high window length

@@

* increasing network connectivity in summer when the window position is moved - these seasons are more similar than the original window position
* same theme shown in the connective redundancy
* quite variable layer similarity, not sure what to pull out of that one
* increased graph strength for winter down the middle, with generally increasing summer layers - again where the season is including more shoulder season potentially

>>>>

<!-- landcover resolution
* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
* decreasing winter lichen relevance because the degree + number of edges decreased
-->

<!-- nobs 
* common, though at different points - more observations until stabilizing
* we dont see the stabilizing/full plateau for connective redundancy but appears to be coming.. 
* still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations
-->

<!-- win  length
* increasing window length = increasingly similar layers and increasingly redundant edges. more individuals have the opportunity to interact
* increasing window length also leads to increasing similarity between seasons because seasons are less well defined/include more shoulder seasons
* decreasing graph strength at the upper end of window length in winter showing again inclusion of more shoulder season
* layers are more similarly relevant at high window length
-->

<!-- win position
* increasing network connectivity in summer when the window position is moved - these seasons are more similar than the original window position
* same theme shown in the connective redundancy
* quite variable layer similarity, not sure what to pull out of that one
* increased graph strength for winter down the middle, with generally increasing summer layers - again where the season is including more shoulder season potentially
-->

<!--
## Each metric's interpretation
* Degree: the number of direct connections an individual has to other individuals in the network. High degree = connected to many indviduals in a single layer. Low degree = not connected to many individuals in a single layer.

@@

@@

<!-- TODO: RO first sentence... -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open. *There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**. B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations. C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers. D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.

@@

@@
